---
title: "historical_review_distribution"
author: "Group 06"
date: "3/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Create a set per neighbourhood for ADE vs year round
## Create a dataframe including only the ADE reviews
### Create a subset for the dates incl 2 weeks after ade
```{r Create a subset for ADE}
ade_all_reviews <- subset(reviews_cleaned, date> "2021-10-13" & date < "2021-10-31")
```
### Count amount reviews per listing ADE 2021
#### Detach dplyr and load plyr
```{r switch packages2, warning=FALSE, message=FALSE}
detach(package:dplyr)
library(plyr)
```
### Count the number of reviews
```{r count the reviews for ADE, message=FALSE}
ade_amount_reviews <- ade_all_reviews %>% count("listing_id")
```
#### Detach plyr and load dplyr
```{r switch packages3, warning=FALSE, message=FALSE}
detach(package:plyr)
library(dplyr)
```
### Select the variables 
```{r select the listing variables for the review comparison}
new_listings <- adam_listings %>% select(id, neighbourhood_cleansed)
```
### Joined the dataframes for listings and counted reviews together
```{r join the listing variables and reviews for ADE together}
ade_review_hood <- ade_amount_reviews %>%
  inner_join(new_listings, by = c("listing_id" = "id"))
```
#### Detach plyr and load dplyr
```{r switch packages4, warning=FALSE, message=FALSE}
detach(package:dplyr)
library(plyr)
```
### Count reviews per neighbourhood during ADE
```{r count ADE reviews per neighbourhood , message=FALSE}
ade_count_review_hood <- ade_review_hood %>% count("neighbourhood_cleansed")
```
## Create a dataset for all the reviews of 2021 excluding ADE
### Create subsets of review data for all the days excluding ade + 2 weeks after the event
```{r create subsets for reviews excluding ADE}
b_ade_reviews <- subset(reviews_cleaned, date> "2021-01-01" & date < "2021-10-12")
a_ade_reviews <- subset(reviews_cleaned, date> "2021-11-01" & date < "2021-12-31")
```
#### Bind the subsets together
```{r bind the two files excluding ADE data together}
not_ade_reviews <- rbind(b_ade_reviews, a_ade_reviews)
```
### Count amount reviews per listing for all of 2021 excluding ade + 2 weeks after the event
```{r count number of reviews excludign ADE, message=FALSE}
not_amount_reviews <- not_ade_reviews %>% count("listing_id")
```
#### Detach plyr and load dplyr
```{r switch package5, warning=FALSE, message=FALSE}
detach(package:plyr)
library(dplyr)
```
### Join the dataframes for listings and counted reviews together
```{r join the dataframes for listings and reviews excluding ade}
not_review_hood <- not_amount_reviews %>%
  inner_join(new_listings, by = c("listing_id" = "id"))
```
#### Detach dplyr and load plyr
```{r switch package6, warning=FALSE, message=FALSE}
detach(package:dplyr)
library(plyr)
```
### Count reviews per neighbourhood for all of 2021 excluding ade + 2 weeks after the event
```{r count reviews per neigbourghood for dates excludign ADE, message=FALSE}
not_count_review_hood <- not_review_hood %>% count("neighbourhood_cleansed")
```
#### Detach plyr and load dplyr
```{r switch package7, warning=FALSE, message=FALSE}
detach(package:plyr)
library(dplyr)
```
## Join the datasets (ade vs not ade) together
```{r join the data sets ADE vs not ADE together}
reviews_event <- ade_count_review_hood %>%
  inner_join(not_count_review_hood, by = c("neighbourhood_cleansed" = "neighbourhood_cleansed"), suffix = c("_ade", "_year_round"))
```
## Mutate extra columns
```{r mutate the columns}
reviews_event <-reviews_event %>% mutate(ADE_reviews = freq_ade / freq_year_round)
reviews_event <-reviews_event %>% mutate(ADE_per_neigbbourhood = reviews_event$freq_ade/sum(reviews_event$freq_ade)*100)
reviews_event <-reviews_event %>% mutate(NOT_ADE_per_neigbbourhood = reviews_event$freq_year_round/sum(reviews_event$freq_year_round)*100)
```
## Create overviews of the data
### Create an overview for reviews per week
```{r overview reviews per week, message=FALSE}
revperweek <- adam_reviews_pw  %>% group_by(weeks) %>% summarize(nr_comments = sum(comments, NA.rm=FALSE))
```
### Create an overview for reviews per day
```{r overview reviews per day, message=FALSE}
revperday <-  adam_reviews_pw  %>% group_by(date) %>% summarize(nr_comments = sum(comments, NA.rm=FALSE))
```
### Create an overview for reviews by neighbourhood per day
```{r overview reviews by neighbourhood per day, message=FALSE}
revperday_neigbourhood <- adam_reviews %>% group_by(date, neighbourhood_cleansed) %>% summarize(nr_comments = sum(comments, na.rm=TRUE))
```