---
title: "Analysis_file"
author: "Group 06"
date: ''
output:
  word_document: default
  pdf_document: default
  html_document: default
---

# set up for r
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Download the right packages for analysis
```{r install packages}
install.packages("ggplot2",repos = "http://cran.us.r-project.org")
install.packages("ggfortify",repos = "http://cran.us.r-project.org")
install.packages("broom",repos = "http://cran.us.r-project.org")
install.packages("dplyr",repos = "http://cran.us.r-project.org")
install.packages("stargazer",repos = "http://cran.us.r-project.org")
install.packages("gt",repos = "http://cran.us.r-project.org")
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
install.packages("glue",repos = "http://cran.us.r-project.org")
install.packages("ggiraphExtra",repos = "http://cran.us.r-project.org")
```
### Load the right packages for analysis
```{r run library functions, warning=FALSE, message=FALSE}
library(ggplot2)
library(ggfortify)
library(broom)
library(dplyr)
library(stargazer)
library(gt)
library(tidyverse)
library(glue)
library(ggiraphExtra)
```
### Part 1 of analysis: screening of the entire year 
# This part of the report is meant to showcase the amount of reviews in the year of 2021 and before

# Overview of total reviews left by guests throughout the year of 2021-line chart
```{r plot 1}
ggplot(revperweek, aes(x = weeks, y=nr_comments)) + geom_line() + 
  geom_hline(yintercept = mean(revperday$nr_comments)*7, color="red") + theme_light() + ggtitle("Number of weekly reviews 2021") +  ylab("Review count") + xlab("week number")
```
# Daily reviews during the ADE review period 2021-bar chart
```{r plot 2, echo=FALSE}
ggplot(ade_all_reviews, aes(x = date)) + geom_bar(stat = "count")
```
# Daily reviews during 2021-bar chart
```{r plot 3}
ggplot(adam_reviews, aes(x = date)) + geom_bar(stat = "count")
```
# Daily reviews during 2021-line chart
```{r plot 4}
ggplot(revperday, aes(x = date, y=nr_comments)) + geom_line() + 
  geom_hline(yintercept = mean(revperday$nr_comments), color="red") + theme_light() + ggtitle("Number of daily reviews 2021") +  ylab("Review count") + xlab("date")
```
# Total reviews left by guests throughout the year of 2021 with ADE time marked
```{r plot 5}
ggplot(data = revperweek, mapping = aes(x = weeks, y = nr_comments)) + geom_line()+ geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_light() + ggtitle("ADE review time 2021") +  ylab("Review count") + xlab("week number")
```
# Total reviews left by guests throughout the year of 2018/2019/2020 with ADE time marked
# with markings of the ADE time period when a review is possible #line chart per week highlighted during ADE review time 2021
```{r plot 6}
ggplot(reviews_per_week20, aes(x = weeks, y= reviews)) + geom_line() + geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_light() + ggtitle("ADE review time 2021") +  ylab("Review count") + xlab("week number")

ggplot(reviews_per_week19, aes(x = weeks, y= reviews)) + geom_line() + geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_light() + ggtitle("ADE review time 2021") +  ylab("Review count") + xlab("week number")

ggplot(reviews_per_week18, aes(x = weeks, y= reviews)) + geom_line() + geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_light() + ggtitle("ADE review time 2021") +  ylab("Review count") + xlab("week number") 
```
## plot amount of reviews per neighbourhood throughout the year-layer chart
## info neighbourhoods #1-centre #2-north #3-east #4-south #5-west #6-new_west #7-southeast
```{r plot 7 reviews per neighbourhood, echo=FALSE}
p <- ggplot(revperday_neigbourhood, aes(x = date, fill = neighbourhood_cleansed))
head(revperday_neigbourhood)

p + geom_area(stat = "bin") +
  scale_fill_brewer(palette="Dark2") + theme_light() +
  ggtitle("Daily reviews per neighbourhood 2021")
```
## table of the amount of reviews per neighbourhood
```{r plot 8}
reviews_event %>% 
  gt() %>% 
  tab_header( 
    title = md("**Amsterdam**"),
    subtitle = md("Amount of reviews per neighbourhoods 2021")
  )
```
### Part 2 of analysis: Regression (based on the building block) 
# Regression: frequency of reviews as DV and neighbourhoods and price as IV
```{r plot 9 regression, echo=FALSE}
mdl_reviews2_wprice <- lm(freq~as.factor(neighbourhood_cleansed)+price, data=new_reviews)
```
# 1. evaluate linear model assumptions
```{r plot 10}
autoplot(
  mdl_reviews2_wprice,
  which = 1:3,
  nrow = 1,
  ncol = 3
)
```
## outliers filter
#  If a listing has a high frequency of reviews in one year, it is considered an outlier
# filter on frequency anmount determimed by Cook's distance
# filter on price set manually at cut-off point of 700
```{r plot 11}
nooutliers_wprice <- new_reviews %>%
    filter(freq != 333, freq != 270, freq != 249, freq != 225, freq != 175, freq != 127, price<700)
```
# regression without outliers
```{r}
mdl_nooutliers_wprice <- lm(freq~as.factor(neighbourhood_cleansed)+price, data=nooutliers_wprice)
```
# 2.outlier screening
```{r plot 12}
freq_influence_wprice <- mdl_reviews2_wprice %>%
  augment() %>%
  select(freq,price, "as.factor(neighbourhood_cleansed)", leverage = .hat, cooks_dist = .cooksd) %>%
  arrange(desc(cooks_dist)) %>%
  head()
```
## table with summary of the outliers
```{r plot 13}
freq_influence_wprice %>% 
  gt() %>% 
  tab_header( 
    title = md("**Outliers in model summary**"),
  )
```
# plot of Cook's distance outliers included-plot
```{r plot 15}
plot(mdl_reviews2_wprice, 4)
plot(mdl_reviews2_wprice, 5)
```
# plot cook's distance outliers not included-plot
```{r plot 16}
plot(mdl_nooutliers_wprice, 4)
plot(mdl_nooutliers_wprice, 5)
```
# 3. #model reporting with summary of the regresssion model with/without outliers
```{r plot 17}
stargazer(mdl_reviews2_wprice, mdl_nooutliers_wprice,
          title = "Figure 1: Car's stop distance increases as speed increases",
          dep.var.caption = "Frequency of reviews",  
          dep.var.labels = "",  
          covariate.labels = c("Neigbourhood/price"),  
          column.labels = c("Full model", "Outlier excluded"),
          notes.label = "Significance levels",  
          type="html",
          out="output.html"  
)
```
## plot w/o outliers
```{r plot 18}
autoplot(
  mdl_nooutliers_wprice,
  which = 1:3,
  nrow = 1,
  ncol = 3
)
```
#4.
# linear relationship of model per neighbourhood-graph
```{r plot 19 }
#4 relationship
#with outliers
ggplot(new_reviews,aes(y=freq,x=price,color=neighbourhood_cleansed))+geom_point()+stat_smooth(method="lm",se=FALSE) + ylab("review frequency per listing") + xlab("price")
View(new_reviews)
```
# linear relationship of model per neighbourhood outliers excluded-graph
```{r plot 20}
ggplot(nooutliers_wprice,aes(y=freq,x=price,color=neighbourhood_cleansed))+geom_point()+stat_smooth(method="lm",se=FALSE)  + ylab("review frequency per listing") + xlab("price")
```
