---
title: "Analysis_file"
author: "Group 06"
date: ''
output:
  word_document: default
  pdf_document: default
  html_document: default
---
# set up for r
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### run the packages 
```{r install packages}
install.packages("ggplot2",repos = "http://cran.us.r-project.org")
install.packages("ggfortify",repos = "http://cran.us.r-project.org")
install.packages("broom",repos = "http://cran.us.r-project.org")
install.packages("dplyr",repos = "http://cran.us.r-project.org")
install.packages("stargazer",repos = "http://cran.us.r-project.org")
install.packages("gt",repos = "http://cran.us.r-project.org")
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
install.packages("glue",repos = "http://cran.us.r-project.org")
install.packages("ggiraphExtra",repos = "http://cran.us.r-project.org")
```
### Load the right packages for analysis
```{r run library functions, warning=FALSE, message=FALSE}
library(ggplot2)
library(ggfortify)
library(broom)
library(dplyr)
library(stargazer)
library(gt)
library(tidyverse)
library(glue)
library(ggiraphExtra)
```
## Part 1 of analysis: screening of the entire year 
# This part of the report is meant to showcase the amount of reviews in the year of 2021 and give a basic analysis of the neighbourhoods in Amsterdam during the year of 2021

# Overview of total reviews left by guests throughout the year of 2021-line chart per week 
```{r plot 1}
ggplot(revperweek, aes(x = weeks, y=nr_comments)) + geom_line() + 
  geom_hline(yintercept = mean(revperday$nr_comments)*7, color="red") + theme_classic() + ggtitle("Number of weekly reviews 2021") +  ylab("Review count") + xlab("week number")
```
# Daily reviews during the ADE review period 2021-bar chart 
```{r plot 2, echo=FALSE}
ggplot(ade_all_reviews, aes(x = date)) + geom_bar(stat = "count") + ggtitle("Bar chart during ADE period 2021")
```
# Daily reviews during 2021-bar chart
```{r plot 3}
ggplot(adam_reviews, aes(x = date)) + geom_bar(stat = "count") + ggtitle("Bar chart during 2021")
```
# Daily reviews during 2021-line chart
```{r plot 4}
ggplot(revperday, aes(x = date, y=nr_comments)) + geom_line() + 
  geom_hline(yintercept = mean(revperday$nr_comments), color="red") + theme_classic() + ggtitle("Number of daily reviews 2021") +  ylab("Review count") + xlab("date")
```
# Total reviews left by guests throughout the year of 2021 with ADE time marked-plot
```{r plot 5}
ggplot(data = revperweek, mapping = aes(x = weeks, y = nr_comments)) + geom_line()+ geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_classic() + ggtitle("ADE review period 2021") +  ylab("Review count") + xlab("week number")
```
# Total reviews left by guests throughout the year of 2018/2019/2020 with ADE time marked
# Overview of total reviews left by guests throughout the year 2018/2019/2020-plot with marking-plot
```{r plot 6}
ggplot(reviews_per_week20, aes(x = weeks, y= reviews)) + geom_line() + geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_classic() + ggtitle("ADE review period 2020") +  ylab("Review count") + xlab("week number")
ggplot(reviews_per_week19, aes(x = weeks, y= reviews)) + geom_line() + geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_classic() + ggtitle("ADE review period 2019") +  ylab("Review count") + xlab("week number")
ggplot(reviews_per_week18, aes(x = weeks, y= reviews)) + geom_line() + geom_area(mapping = aes(x = ifelse(weeks>41 & weeks< 45 , weeks, 0)), fill = "red") + xlim(1, 48) + theme_classic() + ggtitle("ADE review period 2018") +  ylab("Review count") + xlab("week number") 
```
## plot amount of reviews per neighbourhood throughout the year 2021-plot
# info neighbourhoods 1-centre 2-north 3-east 4-south 5-west 6-new_west 7-southeast
```{r plot 7 reviews per neighbourhood, echo=FALSE}
p <- ggplot(revperday_neigbourhood, aes(x = date, fill = neighbourhood_cleansed))
head(revperday_neigbourhood)
p + geom_area(stat = "bin") +
  scale_fill_brewer(palette="Dark2") + theme_classic() +
  ggtitle("Daily reviews per neighbourhood 2021") 
```
# amount of reviews per neighbourhood-table
```{r plot 8}
reviews_event %>% 
  gt() %>% 
  tab_header( 
    title = md("**Amsterdam**"),
    subtitle = md("Amount of reviews per neighbourhoods 2021")
  )
```
## Part 2 of analysis: Regression (based on the regression building block) 
# regression analysis: review count (daily) per neighbourhood and if ade is going on yes/no with  interaction variable of ade on neighbourhoods
```{r plot 9 regression, echo=FALSE}
regression_ade <- lm(reviews~as.factor(neighbourhood_cleansed)+avg_price+as.factor(room_type)+ade+ade*as.factor(neighbourhood_cleansed), data=new_reviews_ade)
summary(regression_ade) 
```
# removing outliers from model (avg_price is the reference)
```{r}
nooutliers_nra <- new_reviews_ade_log %>%
  filter(avg_price != 112.2703, avg_price != 106.2157, avg_price != 249, avg_price != 114.2738, avg_price != 890.0000, avg_price != 325.0000, avg_price != 224.6087)
```
# removing outliers from model with logarithmic transformation 
```{r}
nooutliers_nral <- new_reviews_ade_log %>%
  filter(avg_price != 112.2703, avg_price != 106.2157, avg_price != 249, avg_price != 114.2738, avg_price != 890.0000, avg_price != 325.0000, avg_price != 224.6087)
```
#regression with outliers out of model
```{r}
regression_ade_log_nooutliers <- lm(reviews~as.factor(neighbourhood_cleansed)+avg_price+as.factor(room_type)+ade+ade*as.factor(neighbourhood_cleansed), data=nooutliers_nra)
summary(regression_ade) 
```
#regression with lograrithmic transformation of the "reviews" variable 
```{r}
regression_ade_log <- lm(log(reviews)~as.factor(neighbourhood_cleansed)+as.factor(room_type)+ade+ade*as.factor(neighbourhood_cleansed), data=new_reviews_ade_log)

```
#regression with Logarithmic transformation and outliers out of model
```{r}
regression_ade_log_nooutliers <- lm(log(reviews)~as.factor(neighbourhood_cleansed)+as.factor(room_type)+ade+ade*as.factor(neighbourhood_cleansed), data=nooutliers_nral)
```
# 1. evaluate linear model assumptions
```{r plot 10}
autoplot(
  regression_ade,
  which = 1:3,
  nrow = 1,
  ncol = 3
)
```
# making a log transformation in the model
```{r}
autoplot(
  regression_ade_log,
  which = 1:3,
  nrow = 1,
  ncol = 3
)
```
# plot with logarithmic transformation and outliers removed
```{r}
autoplot(
  regression_ade_log_nooutliers,
  which = 1:3,
  nrow = 1,
  ncol = 3
)
```
# 2 outlier screening
```{r plot 11}
nooutliers_wprice <- new_reviews %>%
    filter(freq != 333, freq != 270, freq != 249, freq != 225, freq != 175, freq != 127, price<700)
```
# regression without outliers
```{r}
mdl_nooutliers_wprice <- lm(freq~as.factor(neighbourhood_cleansed)+price, data=nooutliers_wprice)
```
# 2.outlier screening
```{r plot 12}
regression_ade_outliers <- regression_ade %>%
  augment() %>%
  select("as.factor(room_type)", "as.factor(neighbourhood_cleansed)", ade, avg_price, leverage = .hat, cooks_dist = .cooksd) %>%
  arrange(desc(cooks_dist)) %>%
  head()
```
# visualize outliers in table
```{r plot 13}
regression_ade_outliers %>% 
  gt() %>% 
  tab_header( 
    title = md("**Outliers in model summary**"),
  )
```
# Additional plots outliers
# before 
```{r plot 15}
plot(regression_ade, 4)
plot(regression_ade, 5)
```
# after removing outliers 
```{r plot 16}
plot(regression_ade_log_nooutliers, 4)
plot(regression_ade_log_nooutliers, 5)
```
# 3. #model reporting with summary of the regresssion model with/without outliers
```{r plot 17}
stargazer(regression_ade, regression_ade_log, regression_ade_log_nooutliers,
          title = "Figure 1: Review count per neighbourhood and ADE",
          dep.var.caption = "Frequency of reviews",  
          dep.var.labels = "",  
          covariate.labels = c("Neigbourhood/price"),  
          column.labels = c("Full model", "Logarithmic transformation", "Outliers excluded"),
          notes.label = "Significance levels",  
          type="html",
          out="output.html"  
)
```
#4 Visualize relationships between variables
# linear relationship of model per neighbourhood outliers excluded-graph
```{r plot 20}
new_reviews_ade %>% 
  mutate(ade = as.factor(ade)) %>% 
  ggplot(mapping = aes(x = neighbourhood_cleansed, fill = ade)) +
  geom_bar()
```